Response to reviewers

### 2025-07-04 src/docs_paper-jtb/revisions.Rmd
Add clarification about LGM
Include equation numbers
Better grammar

> Equations...

@@

We agree this is an interesting area for future work, and have added a sentence to Section 6.1.2. discussing the possibility of doing this in `TMB`:

>>>>

> Section 3 (e.g. Equations(8) to (11)) shows that the Naomi model involves many-to-one mappings of latent field components to the structured additive predictor for each response. Because of this, the Naomi model cannot be written as an LGM of the form described in Section 2.1, but can be written as an ELGM.

@@

We agree that this is an interesting area for future work, and have added a sentence to Section 6.1.2. discussing the possibility of doing this in `TMB`:
